Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, 
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
However, the sizes of MCCs are almost a factor of two smaller. This likely suggest that the sizes of \highz molecular gas structures reported in the literature
are limited by the spatial resolution. 
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lies along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion 
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.

>>>>

In this section, we compare the observable quantities of MCCs obtained from the simulations (e.g., $\sigma_{\rm gas}$, $R$, $M_{\rm gas}$, $\Sigma_{\rm gas}$) with those of molecular gas structures from \obs at lower redshift.
%%
%We exclude the biggest MCC identified in each evolutionary stage, which correspond to the main disk of \flower (i.e., the top right cluster of points in the linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}).
The velocity dispersion of MCCs in \flower is similar to those observed in $z$\ssim2 spatially resolved studies of gas-rich star-forming galaxies, 
spanning a range of $\sigma_{\rm gas}\simeq$\,20$-$80\,\kms (\Fig{larsons_single}; see e.g., \citealt{Swinbank11a}). 
However, the sizes of MCCs are almost a factor of two smaller. This
% mm2 likely suggest
    suggests 
that the sizes of \highz molecular gas structures reported in the literature
are
% mm2
   probably
limited by the spatial resolution. 
%
The velocity dispersions of some MCCs are also comparable to the most turbulent gas clouds observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}), which lie along the locus of $\sigma_{\rm gas}\propto R^{0.56}$. Such high velocity dispersion 
in \flower is dominated by non-thermal energy (\Fig{vv}) and results from the injection of kinetic energy from recent \SF as \flower is assembling its stellar mass (given the high Mach numbers of MCCs; \Sec{distribution}). In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, \flower has assembled a stellar mass of $M_\star$\eq7.5\E{9}\,\Msun.
%mm2
   This contrasts with \citet{Krumholz18}, who show that numerical models and analytic arguments point to
   feedback generally not being able to produce velocity dispersions of more than 10--20 km~s$^{-1}$, with
   higher velocities likely being produced by Toomre instability driven radial inflow.
